### 2022-07-07 paper/Chapters/Chapter05.tex
update ag model

%% nnnn exp
\section{Surface Normal Inference based on Depth Map}
The goal of surface normal inference is to calculate the tangent surface normal map $ N $ from a single depth map $ D $. A network named Gated Convolution Neural Network (GCNN) ( \ref{gcnn}) is trained and is compared with similar approaches. We evaluate the performance of the model in dataset ``synthetic50-5" introduced in  \ref{ch:04} including 5K depth maps with size  $ 512\times512\times3 $ for training. All the depth maps add simulated noise as introduced in \ref{sec:noise}. The training pipeline use batch size $ 8 $,  Adam optimizer (\cite{adam}), learning rate of  $ 1\times10^{-3} $, penalty-l2 loss(see \ref{sec:loss}). The output is directly the tangent normal in range $ \left[-1,1\right] $. The output and input has the same shape.

@@

The visual evaluation on model GCNN shown in Figure \ref{fig:gcnn-eval-synthetic-full}.

%% a detailed analyis of this figure
It is

The evaluation visualization on test dataset is shown in Figure \ref{fig:gcnn-eval-synthetic}. Figure \ref{fig:gcnn-eval-synthetic-zoom-in} zooms in the hindhead area of the dragon object which provides a closer comparison with the ground-truth.
\begin{figure}[th]
	\centering
	\begin{subfigure}[b]{0.15\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_input.png}
		\caption{Input}
	\end{subfigure}
	\begin{subfigure}[b]{0.15\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_normal_GT.png}
		\caption{GT}
	\end{subfigure}
		\begin{subfigure}[b]{0.15\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_normal_GCNN.png}
		\caption{GCNN}
	\end{subfigure}
		\begin{subfigure}[b]{0.15\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_normal_SVD.png}
		\caption{SVD}
	\end{subfigure}
	\begin{subfigure}[b]{0.15\linewidth}
	\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_error_GCNN.png}
	\caption{}
	\end{subfigure}
	\begin{subfigure}[b]{0.15\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_error_SVD.png}
		\caption{}
	\end{subfigure}
	\caption{Zoom in of dragon object evaluation.}
	\label{fig:gcnn-eval-synthetic-zoom-in}
\end{figure}

>>>>

%% nnnn exp
\section{Surface Normal Inference based on Depth Map}
The goal of surface normal inference is to calculate the tangent surface normal map $ N $ from a single depth map $ D $. A network named Gated Convolution Neural Network (GCNN) ( \ref{gcnn}) is trained and is compared with similar approaches. We evaluate the performance of the model in dataset ``synthetic50-5" introduced in  \ref{ch:04} including 5K depth maps with size  $ 512\times512\times3 $ for training. All the depth maps add simulated noise as introduced in \ref{sec:noise}. The training pipeline use batch size $ 8 $,  Adam optimizer (\cite{adam}), learning rate of  $ 1\times10^{-3} $, penalty-l2 loss. The output is directly the tangent normal in range $ \left[-1,1\right] $. The output and input has the same shape.

@@

The evaluation visualization on test dataset is shown in Figure \ref{fig:gcnn-eval-synthetic}. As shown in the picture, GCNN model 
Figure \ref{fig:gcnn-eval-synthetic-zoom-in} zooms in the hindhead area of the dragon object which provides a closer comparison with the ground-truth.
\begin{figure}[th]
	\centering
	\includegraphics[width=0.15\linewidth]{./Figures/comparison/fancy_eval_6_point_cloud_noise.png}
	\includegraphics[width=0.15\linewidth]{./Figures/comparison/fancy_eval_6_groundtruth.png}
	\includegraphics[width=0.15\linewidth]{./Figures/comparison/fancy_eval_6_normal_GCNN3-32-512.png}
	\includegraphics[width=0.15\linewidth]{./Figures/comparison/fancy_eval_6_normal_SVD.png}
	\includegraphics[width=0.15\linewidth]{./Figures/comparison/fancy_eval_6_error_GCNN3-32-512.png}
	\includegraphics[width=0.15\linewidth]{./Figures/comparison/fancy_eval_6_error_SVD.png}
	\caption{GCNN Normal Inference on Synthetic Dataset (object: dragon) From left to right: Input vertex map, ground-truth, GCNN normal map, SVD normal map, GCNN error map, SVD error map}
	\label{fig:gcnn-eval-synthetic}
\end{figure}

\begin{figure}[th]
	\centering
	\begin{subfigure}[b]{0.15\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_input.png}
		\caption{Input}
	\end{subfigure}
	\begin{subfigure}[b]{0.15\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_normal_GT.png}
		\caption{GT}
	\end{subfigure}
		\begin{subfigure}[b]{0.15\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_normal_GCNN.png}
		\caption{GCNN}
	\end{subfigure}
		\begin{subfigure}[b]{0.15\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_normal_SVD.png}
		\caption{SVD}
	\end{subfigure}
	\begin{subfigure}[b]{0.15\linewidth}
	\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_error_GCNN.png}
	\caption{}
	\end{subfigure}
	\begin{subfigure}[b]{0.15\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_error_SVD.png}
		\caption{}
	\end{subfigure}
	\caption{Zoom in of dragon object evaluation.}
	\label{fig:gcnn-eval-synthetic-zoom-in}
\end{figure}
